---
title: "Figure 4. Function enrichment results of methylated genes in P.aeruginosa strains."
author: "Liu Jihong"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Clean workspace
rm(list=ls()) 
# Set output directory
output_dir="./"
```

## Function Enrichment
Methylated genes refer to genes with corresponding DNA methylation modification in transcriptional regulatory regions. The most enriched functional terms of genes associated with: (a) the TRGANNNNNNTGC motif sites in TBCF; 

```{r}
table<-read.table("../data/GCANNNNNNTCYA_TRGANNNNNNTGC_RR_fun-4.txt",header = T, sep = "\t")
GoFunctionTerms <-table
## numbers as data on x axis

GoFunctionTerms$number <- factor(rev(1:nrow(GoFunctionTerms)))
GO_term_order=factor(as.integer(GoFunctionTerms$number),labels=GoFunctionTerms$Pathway)

CPCOLS <- c("#8DA1CB", "#FD8D62", "#66C3A5","#cc6666")
p_GoFunctionTerms <-GoFunctionTerms
library(ggplot2)
p1 <- ggplot(data=p_GoFunctionTerms, aes(x=GO_term_order, y=Count, fill=Category)) +
  geom_bar(stat="identity", width=0.8) + coord_flip() + 
  scale_fill_manual(values = CPCOLS) + theme_test() +
  xlab("Pathways") + 
  theme(axis.text=element_text(face = "bold", color="gray50",size = 17)) +
  theme(title = element_text(size = 17))+
  theme(legend.text = element_text(size = 17))+
  labs(title = "The Most Enriched Function Terms")
ggsave("TBCF-TRGA.eps", device = "eps", width=20, height=20)
ggsave("TBCF-TRGA.pdf", width=20, height=20)




```

(b) the RCCANNNNNNNTGAR motif sites in TBCF;
```{r}

table<-read.table("../data/RCCANNNNNNNTGAR_YTCANNNNNNNTGGY_RR.fun-4.txt",header = T, sep = "\t")
GoFunctionTerms <-table
## numbers as data on x axis

GoFunctionTerms$number <- factor(rev(1:nrow(GoFunctionTerms)))
GO_term_order=factor(as.integer(GoFunctionTerms$number),labels=GoFunctionTerms$Pathway)

CPCOLS <- c("#FD8D62", "#66C3A5","#cc6666")
library(ggplot2)
p2 <- ggplot(data=GoFunctionTerms, aes(x=GO_term_order, y=Count, fill=Category)) +
  geom_bar(stat="identity", width=0.8) + coord_flip() + 
  scale_fill_manual(values = CPCOLS) + theme_test() +
  xlab("Pathways") + 
  theme(axis.text=element_text(face = "bold", color="gray50",size = 17)) +
  theme(title = element_text(size = 17))+
  theme(legend.text = element_text(size = 17))+
  labs(title = "The Most Enriched Function Terms")

p2
ggsave("TBCF-RCCA.eps", device = "eps", width=20, height=20)
ggsave("TBCF-RCCA.pdf", width=20, height=20)

```

 (c) the CCCGAG motif sites in LYSZa7; 
 

```{r}

table<-read.table("../data/CCCGAG.RR.fun-4.txt",header = T, sep = "\t")
GoFunctionTerms <-table
GoFunctionTerms<-GoFunctionTerms[-10,]
## numbers as data on x axis

GoFunctionTerms$number <- factor(rev(1:nrow(GoFunctionTerms)))
GO_term_order=factor(as.integer(GoFunctionTerms$number),labels=GoFunctionTerms$Pathway)

CPCOLS <- c("#8DA1CB","#FD8D62", "#66C3A5","#cc6666")
library(ggplot2)
p4 <- ggplot(data=GoFunctionTerms, aes(x=GO_term_order, y=Count, fill=Category)) +
  geom_bar(stat="identity", width=0.8) + coord_flip() + 
  scale_fill_manual(values = CPCOLS) + theme_test() +
  xlab("Pathways") + 
  theme(axis.text=element_text(face = "bold", color="gray50",size = 17)) +
  theme(title = element_text(size = 17))+
  theme(legend.text = element_text(size = 17))+
  labs(title = "The Most Enriched Function Terms")

p4
ggsave("LYSZa7-CCCGAG.eps", device = "eps", width=20, height=20)
ggsave("LYSZa7-CCCGAG.pdf", width=20, height=20)

```
 
 
 (d) the AGGNNNNNRTGT motif sites in LYSZa7. 
```{r}
table<-read.table("../data/ACAYNNNNNCCT_AGGNNNNNRTGT_RR.fun-4.txt",header = T, sep = "\t")
GoFunctionTerms <-table
## numbers as data on x axis

GoFunctionTerms$number <- factor(rev(1:nrow(GoFunctionTerms)))
GO_term_order=factor(as.integer(GoFunctionTerms$number),labels=GoFunctionTerms$Pathway)

CPCOLS <- c("#8DA1CB", "#FD8D62", "#66C3A5","#cc6666")
p_GoFunctionTerms <-GoFunctionTerms
library(ggplot2)
p3 <- ggplot(data=p_GoFunctionTerms, aes(x=GO_term_order, y=Count, fill=Category)) +
  geom_bar(stat="identity", width=0.8) + coord_flip() + 
  scale_fill_manual(values = CPCOLS) + theme_test() +
  xlab("Pathways") + 
  theme(axis.text=element_text(face = "bold", color="gray50",size = 17)) +
  theme(title = element_text(size = 17))+
  theme(legend.text = element_text(size = 17))+
  labs(title = "The Most Enriched Function Terms")

p3
ggsave("LYSZa7-ACAY.eps", device = "eps", width=20, height=20)
ggsave("LYSZa7-ACAY.pdf", width=20, height=20)

```



